# Train and get the Model: trainModel() and getModel() functions

In order to display the DFG, it is necessary at first to call the **trainModel()** function. 
This function enables the creation of the NxN matrix, which, as we discussed in the preceding section, provides the basis for the creation of the graph.

```{r,echo=FALSE, eval=TRUE, include=TRUE, results='hide', warning=FALSE, message=FALSE}
library(pMineR)
objDL<-dataLoader()
objDL$load.csv(nomeFile = "EventLog1.csv",IDName = "ID",EVENTName= "Event",dateColumnName="Date",format.column.date = "%Y-%m-%d",quote = ",")
obj.out<-objDL$getData()

param.list<-list()
param.list$considerAutoLoop<-FALSE
param.list$threshold<-0.02
objFOMM<-firstOrderMarkovModel(parameters.list = param.list)
objFOMM$loadDataset(dataList = obj.out)
```
```{r}
objFOMM$trainModel()
```


After doing so, we can use the **getModel()** function, which returns the trained internal FOMM model in terms of:

 - _DFG_;
 - _MMatrix_: the matrix containing the number of cases, from the event associated at the line i to the event associated to the column j;
 - _MMatrix.perc_: the matrix containing the probability to move, from the event associated at the line i to the event associated to the column j.
 
You must specify the kind of output by the **kindOfOutput** input, which allows the following values:

 - **"grViz"** for the DFG.
 - **"MMatrix"**
 - **"MMatrix.perc"**

```{r}
objFOMM$getModel(kindOfOutput ="MMatrix" )

```

```{r}
objFOMM$getModel(kindOfOutput ="MMatrix.perc")
```
```{r}
DFG<-objFOMM$getModel(kindOfOutput ="grViz")
library(DiagrammeR)
grViz(DFG)
```
```{r}

```

The **plot()** function can be used as an alternative to the getModel(kindOfOutput="grViz") method:

```{r}
script<-objFOMM$plot(giveItBack = T)
grViz(script)
```


# Survival Analysis: KaplanMeier() and LogRankTest() function

The fomm class also contains methods for performing the Survival Analysis. 

The first of these functions is KaplanMeier() function, which builds a Kaplan Meier curve through an indicated pathway that the user enters by the function inputs. 

Specifically, the the function  arguments are: 

 - **fromState**: first event of the pathway;
 - **toState**: last event of the pathway;
 - **passingThrough**: array containing the events labels that should be included in the pathay;
 - **passingNotThrough**: array containing the events labels that should NOT be included in the pathay;
 - **PDV**: array representing the event(s) the case must experience in order to become censored
 - **withPatientID**: array which allows to filter by case-ID
 - **UM**: time unit (_default: "mins", possible values: "mins","hours","days","weeks","months"_)
 
```{r}
survival.list<-objFOMM$KaplanMeier(fromState = "Medical Visit",
                                   toState = "death",
                                   passingThrough = "partial resection",
                                   PDVAt = "MedicalVisit",
                                   UM = "weeks")

s1 <- survfit(Surv(time, outcome) ~ 1, data = survival.list$table)
survminer::ggsurvplot(s1)

#also: survminer::ggsurvplot(survival.list$KM,data = survival.list$table)
```
```{r}
survival.list2<-objFOMM$KaplanMeier(fromState = "Medical Visit",
                                   toState = "chemotherapy",
                                   passingThrough = "partial resection",
                                   PDVAt = "MedicalVisit",
                                   UM = "weeks")

s2 <- survfit(Surv(time, outcome) ~ 1, data = survival.list2$table)
survminer::ggsurvplot(s1,palette = "blue")
```

It is possible to compare two Kaplan Meier through a Log Rank test by the **LogRankTest()** function:

```{r}
log.out<-objFOMM$LogRankTest(KM1 = survival.list,KM2 = survival.list2)

log.out$survdiff

```
```{r}
new.df <- rbind(survival.list$table,survival.list2$table)
new.df$KM <- c(rep("KM1",nrow(survival.list$table) ),rep("KM2",nrow(survival.list2$table) ))
survminer::ggsurvplot(fit = log.out$survfit,data = new.df,conf.int = T)
```
 
